---
title: "Assignment1"
output: github_document
---

## Exercise 1: Make a Function 

This function aims to implement the function of `strsplit()` without using this wrapper function and adds the possibility to split and keep the delimiter after or before the given split, or it can help to split between two given splits and keep both.

Input Arguments:

- `x`: character vector, each element of which is to be split. Other inputs, including a factor, will give an error.
  - _Justification_: This is the main argument, a `str` to be processed by this function.
- `split`: character vector (or object which can be coerced to such) containing regular expression(s) to use for splitting. If empty matches occur, in particular if `split` has length 0, `x` is split into single characters. If `split` has length greater than 1, it is recycled along `x`.
  - _Justification_: This is the delimiter.
- `type`: charachter. Either to `remove` or keep the delimiter `before`, `between` or `remove` the split.
  - _Justification_: This is a new feature to determine what kind of function will be realized.
- `perl`: logical. Should Perl-compatible regexps be used? Is `TRUE` for all but `remove`.
  - _Justification_: This is a new feature to determine what kind of function will be realized.  
- `...`: other inputs passed along to `strsplit`.
  - _Justification_: There can also be a parameter to determine whether to match byte-by-byte and the default value is false (matching character-by-character). 

Output:
Return a list of the same length as `x`, the i-th element of which contains the vector of splits of `x[i]`. The list can show the result of `character` split.

```{r}
StrSplitP <- function(x,
                     split,
                     type = "remove",
                     perl = FALSE,
                     ...) {
  
  if (!type %in% c("remove", "before", "after", "between")) {
    stop("type must be remove, after, before or between!")
  }

  if (type == "between" & length(split) != 2) {
    stop("split need no have length two!")
  }
  if (length(split) != 1 & type != "between") {
    split <- split[1]
    warning("there are multiple splits - taking only the first one")
  }

  if (type == "remove") {
    out <- base::strsplit(x = x, split = split, perl = perl, ...)
  } else if (type == "before") {
    out <- base::strsplit(x = x,
                          split = paste0("(?<=.)(?=", split, ")"),
                          perl = TRUE,
                          ...)
  } else if (type == "after") {
    out <- base::strsplit(x = x,
                          split = paste0("(?<=", split, ")"),
                          perl = TRUE,
                          ...)
  } else if (type == "between") {
    out <- base::strsplit(
      x = x,
      split = paste0("(?<=", paste0(split, collapse = ""), ")"),
      perl = TRUE,
      ...)

    index <- lapply(out, endsWith, suffix = paste0(split, collapse = ""))
    index <- lapply(index, function(i) which(i == TRUE) + 1)

    out <- lapply(out, function(i) gsub(paste0(split, collapse = ""),
                                        split[1], i))

    out <- mapply(FUN = function(o, i) {
      o[i] <- paste0(split[2], o[i])
      return(o)
      },
      out, index,
      SIMPLIFY = FALSE)
  }

  return(out)
}
```

## Exercise 2: Document your Function
```{r}
# Split the data
# @param data and the data source to be handled
# @param use the function of StrSplitP to split the data into the pattern you want
# @return the output result

# @examples
# str
# StrSplitP(spitstr, delimiter, type)

# export
# @md
```

## Exercise 3: Include examples
This `StrSplitP()` function is implemented as follows. 
Useful error messages are provided by `stop()` for new parameter `type`, because it should be in four certain types.

Three non-redundant inputs are provided to demonstrate its function:

- `x <- c("3D/MON&SUN")` `strsplit(x, "[/&]", type = "before")`
  - This function can split `x` by the two `split` and preserve them before the separated parts.

```{r}
x <- c("3D/MON&SUN")
StrSplitP(x, "[/&]", type = "before")
```
- `x <- c("3D/MON&SUN")` `strsplit(x, "", type = "before")`
  - This function will be split to single characters if the length of `split` is 0.
  
```{r}
x <- c("3D/MON&SUN")
StrSplitP(x, "", type = "before")
```
- `x <- c("3D/MON&SUN")` `strsplit(x, "S", type = "DK")`
  - This function will give an error message if the type is not the four certain types.
  
```{r error=TRUE}
x <- c("3D/MON&SUN")
StrSplitP(x, "S", type = "DK")
```

## Exercise 4: Test the Function 
`testthat` package should be installed to test this function with three inputs.

```{r}
library(testthat)

x <- c("3D/MON&SUN2D/MON&SUN")
test_that('Strsplit test!', {
  expect_error(StrSplitP(StrSplitP(x, "S", type = "WILLBEERROR")))
  expect_equal(StrSplitP(x, "/", type = "remove"), list(c("3D","MON&SUN2D","MON&SUN")))
  expect_equal(StrSplitP(x,""),list(c("3", "D", "/", "M", "O", "N", "&", "S", "U", "N","2", "D", "/", "M", "O", "N", "&", "S", "U", "N")))
})
```

